Legion: Expressing Locality and Independence with Logical Regions

### 2012-08-06 doc/sc2012/legion.tex
Adding stuff for the camera ready version of the SC paper

\author{
\IEEEauthorblockN{Michael Bauer}
\IEEEauthorblockA{Stanford University \\ mebauer@cs.stanford.edu}
\and
\IEEEauthorblockN{Sean Treichler}
\IEEEauthorblockA{StanfordUniversity \\ sjt@cs.stanford.edu}
\and
\IEEEauthorblockN{Elliott Slaughter}
\IEEEauthorblockA{Stanford University \\ slaughter@cs.stanford.edu}
\and
\IEEEauthorblockN{Alex Aiken}
\IEEEauthorblockA{Stanford University \\ aiken@cs.stanford.edu}
}

@@

\input{circuit}
\input{part_fig}
\input{soop}
\input{mapping}
\input{experiments}
\input{related}
%\input{conclusion}

>>>>

\author{
\IEEEauthorblockN{Michael Bauer}
\IEEEauthorblockA{Stanford University \\ mebauer@cs.stanford.edu}
\and
\IEEEauthorblockN{Sean Treichler}
\IEEEauthorblockA{Stanford University \\ sjt@cs.stanford.edu}
\and
\IEEEauthorblockN{Elliott Slaughter}
\IEEEauthorblockA{Stanford University \\ slaughter@cs.stanford.edu}
\and
\IEEEauthorblockN{Alex Aiken}
\IEEEauthorblockA{Stanford University \\ aiken@cs.stanford.edu}
}

@@

\input{circuit}
\input{part_fig}
\input{soop}
\input{mapping}
\input{experiments}
\input{related}
\input{conclusion}

\section*{Acknowledgements}
This research used resources of the Keeneland Computing Facility at the
Georgia Institute of Technology, which is supported by the National
Science Foundation under Contract OCI-0910735.  Michael Bauer was supported
by an NVIDIA Graduate Research Fellowship.
